Reproducible Builds for\\ Computational Research Papers

### 2020-08-19 ms.tex
improve text

\begin{abstract}
	Previous work in reproducibility focused on providing frameworks to help writing reproducible research papers, however without taking in consideration the cost of extra work by the authors to make their paper reproducible and by the reviewers to verify the paper's reproducibility.
	We propose a simple template for writing computational research papers in \LaTeX\ that are easily verifiable in terms of their reproducibility.
	The template provides a Makefile that allows the verifier to execute the code that reproduces the figures, tables and variables (results) of the paper, which are then used during the \LaTeX\ compilation, to produce a pdf.
	The previous procedure is completed twice and the research paper is verified as reproducible, if and only if the resulted pdf files are identical.
	The two builds are needed to enable comparison between different builds of the same source code such that any non-deterministic stochasticity would produce different pdf files, thus making the paper non-reproducible.
	The reproducibility of a paper can be verified either locally on the machine of the verifier or remotely using Virtual Machines (VMs) in the cloud.
	We release an open source template of `reproducible builds' (RBs) and use it to write and verify the reproducibility of this paper.
\end{abstract}

\section{Introduction}
A research paper is considered reproducible when reviewers are able to reproduce its results, given the data and experimental procedure.
More specifically, computational research reproducibility requires the presence of source code that produces or fetches data from external sources which then transforms into the figures, tables and variables of the paper.
Open sourcing the code and the raw data of a computational research paper helps increasing its reproducibility confidence but it is not enough to verify it.
The use of a template for writing and verifying computational research papers will push the direction towards creating reproducible research, thus tackling the `reproducibility crisis' problem.

@@

The proposed template can be applied on computational research papers that are written in \LaTeX~\cite{lamport1994latex} and the `results code' can be executed within a Docker container or a virtual environment.
\LaTeX\ is a typesetting system for publishing high quality research papers, and Docker~\cite{merkel2014docker} is a container system that allows portable execution of a codebase between different operating systems/environments and has shown great promise in reproducible science~\cite{boettiger2015introduction}.
The corresponding Dockerfile can be provided by the researcher or generated by tools such as containerit~\cite{nust2019containerit}.

>>>>

\begin{abstract}
	Previous works in research reproducibility provided frameworks for writing reproducible research papers, however without considering the extra work that needs to be done by the authors to make their paper reproducible and by the reviewers to verify the paper's reproducibility.
	We propose a simple template for writing computational research papers in \LaTeX\ that are easily verifiable in terms of their reproducibility.
	The template contains a Makefile that allows the verifier to execute the code that reproduces the figures, tables and variables (results) of the paper, which are then used during the \LaTeX\ compilation, to produce a pdf.
	The previous procedure is completed twice and the paper is verified as reproducible, if and only if the resulted pdf files are identical.
	The two builds are needed to enable comparison between different builds of the same source code such that any non-deterministic stochasticity would produce different pdf files, thus making the paper non-reproducible.
	The reproducibility of a paper can be verified either locally on the machine of the verifier or remotely using Virtual Machines (VMs) in the cloud.
	We release an open source template of `reproducible builds' (RBs) and use it to write and verify the reproducibility of this paper.
\end{abstract}

\section{Introduction}
A research paper is considered reproducible when reviewers are able to reproduce its results, given the data and experimental procedure.
More specifically, computational research reproducibility requires the presence of source code that produces or fetches data from external sources which then transforms into the figures, tables and variables of the paper.
Open sourcing the code and the raw data of a computational research paper helps increasing the confidence of its reproducibility but it is not enough to verify it.
The use of a template for writing and verifying computational research papers will push the direction towards creating reproducible research, thus tackling the `reproducibility crisis' problem.

@@

The proposed template can be applied on computational research papers written in \LaTeX~\cite{lamport1994latex} and the `results code' can be executed within a Docker container or a virtual environment.
\LaTeX\ is a typesetting system for publishing high quality research papers, and Docker~\cite{merkel2014docker} is a container system that allows portable execution of a codebase between different operating systems/environments and has shown great promise in reproducible science~\cite{boettiger2015introduction}.
The corresponding Dockerfile can be provided by the researcher or generated by tools such as containerit~\cite{nust2019containerit}.
